Uncovering Ferry Traffic Patterns: A Data-Driven Study of Toronto Island Ticket Sales and Redemptions

### 2024-09-27 outputs/paper/paper.qmd
Final draft of the paper: checked and made minor changes to the main text

@@

```{r}
#| label: fig-linePlot2
#| fig-cap: Redemption and Sales Counts Over Time in months
#| warnings: false
#| message: false
#| echo: false
#| fig-width: 8
#| fig-height: 3.5
#| 
# Load necessary libraries
library(ggplot2)
library(dplyr)
library(lubridate)

@@

  # Set symmetrical y-axis limits for both Sales and Redemption
  scale_y_continuous(limits = c(-max_count, max_count),
                     breaks = seq(-max_count, max_count, by = 100000),
                     sec.axis = sec_axis(~ -., name = "Sales Count (dashed lines)")) +

  # Add plot labels
  labs(
    y = "Redemption Count (straight lines)",  # Y-axis for Redemption Count (inverted)
    x = "Month",             # X-axis for Month
    color = "Year"
  ) +

@@

@fig-linePlot3 below compares the sales count and redemption count in year 2021 and 2023. The two side-by-side plots illustrate distinct usage patterns across these years.

```{r}
#| label: fig-linePlot3
#| fig-cap: Redemption and Sales Counts Over Time in 2021 and 2023
#| echo: false
#| warning: false
#| message: false
#| fig-pos: "H"  # Fix the plot in current place when rendered
#| fig-width: 8
#| fig-height: 3

@@

>>>>

The raw data underwent extensive cleaning, including the removal of rows with missing values, conversion of timestamps to a uniform format, and filtering out duplicates and unrealistic values such as negative ticket counts. This process ensured a reliable foundation for subsequent analysis.

@@

```{r}
#| label: fig-linePlot2
#| fig-cap: Redemption and Sales Counts Over Time in months
#| warnings: false
#| message: false
#| echo: false
#| fig-width: 8
#| fig-height: 3.3
#| 
# Load necessary libraries
library(ggplot2)
library(dplyr)
library(lubridate)

@@

  # Set symmetrical y-axis limits for both Sales and Redemption
  scale_y_continuous(limits = c(-max_count, max_count),
                     breaks = seq(-max_count, max_count, by = 100000),
                     sec.axis = sec_axis(~ -., name = "Sales Count (straight lines)")) +

  # Add plot labels
  labs(
    y = "Redemption Count (dashed lines)",  # Y-axis for Redemption Count (inverted)
    x = "Month",             # X-axis for Month
    color = "Year"
  ) +

@@

```{r}
#| label: fig-linePlot3
#| fig-cap: Redemption and Sales Counts Over Time in 2021 and 2023
#| echo: false
#| warning: false
#| message: false
#| fig-width: 8
#| fig-height: 2.8

@@

```
@fig-linePlot3 compares the sales count and redemption count in year 2021 and 2023. The two side-by-side plots illustrate distinct usage patterns across these years.
